%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Solution Engineer/Full-stack Software Developer} % Job title
{\href{https://myrepublic.co.id/}{PT Eka Mas Republik}} % Organization
{Tangerang, Banten} % Location
{December 2022 -- Present} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibilities:
\vspace{5mm}
\begin{cvitems}
\item {Initiate a customer retention management system.}
\item {Support a customer service provisioning/monitoring system.}
\item {Support over-the-top (OTT) media service integration.}
\item {Support a customer self-care application.}
\item {Support the future version of BSS/OSS.}
\item {Support continous integration/continous deployment (CI/CD).}
\item {Support administration of self-hosted GitLab instance.}
\item {Support service deployments on on-premise servers.}
\end{cvitems}
\vspace{5mm}
Technology stacks:
\vspace{5mm}
\begin{cvitems}
\item {PHP/Laravel, JavaScript/Livewire, CSS/Tailwind, MySQL, Redis, Nginx, Postal}
\item {PHP/Slim Framework, JavaScript/JQuery, CSS/Bootstrap, MySQL, RabbitMQ, Apache}
\item {JavaScript/React Native, PHP/Laravel, MySQL, Nginx, Kubernetes}
\item {Java/Quarkus, PostgreSQL, Nginx, Elasticsearch, Logstash, Kibana, Jira}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Front-end Web Developer for \href{https://juraganmaterial.id/}{PT Aneka Juragan Material}} % Job title
{\href{https://www.smooets.com/}{PT Smooets Teknologi Outsourcing}} % Organization
{Bandung, West Java (Hybrid)} % Location
{November 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibility: Support the user registration and blogging features page.
\linebreak
Technology stack: JavaScript/Vue.js, Google Cloud Platform, Strapi, Clarity
\linebreak
Project link: \href{https://juraganmaterial.id/}{https://juraganmaterial.id/}
\linebreak
Memorable experience: I managed to help a co-worker complete the blogging features page, which had been delayed by two weeks, in about 2 days, while I was new to the technology stack and joined the project for less than a week.
}

%------------------------------------------------

\cventry
{Full-stack Web Developer for \href{https://www.edubridge.co.id/}{EduBridge Education Consulting}} % Job title
{} % Organization
{} % Location
{July 2021 -- November 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibilities:
\vspace{5mm}
\begin{cvitems}
\item {Support the future version of marketing website.}
\item {Initiate the company's administration dashboard.}
\end{cvitems}
\vspace{4mm}
Technology stack: PHP/Laravel, JavaScript/Livewire, MySQL, Nginx, Amazon Web Services
\linebreak
Project link: \href{https://www.edubridge.co.id/}{https://www.edubridge.co.id/}
\linebreak
Memorable experience: Our team managed to receive a compliment from the client within the first three months of service.
}

%------------------------------------------------

% \cventry
% {Front-End Web Developer for \href{https://helloakin.com/}{Techlyon Pte Ltd}} % Job title
% {} % Organization
% {} % Location
% {June 2022} % Date(s)
% { % Description(s) of tasks/responsibilities
% Responsibility: Re-designing their \href{https://giveblood.sg/donor-appreciation/}{donor appreciation} web page to include latest information.
% \linebreak
% Most challenging task: to ensure the web page can run responsively on any devices.
% \linebreak
% Technology stack: HTML/CSS, Elementor (Website Builder), WordPress, Amazon Web Services
% \linebreak
% Project link: \href{https://giveblood.sg/donor-appreciation/}{https://giveblood.sg/donor-appreciation/}
% }

%------------------------------------------------

\cventry
{Front-End Web Developer for \href{https://helloakin.com/}{Techlyon Pte Ltd}} % Job title
{} % Organization
{} % Location
{Apr. 2022 -- May 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibility: Build a mini web-based game, i.e. \href{https://giveblood.sg/iron-rich-food/}{Iron-Rich Food Dash}.
\linebreak
% Most challenging task: to ensure the game can fully function perfectly on Apple and Android devices.
% \linebreak
Technology stack: HTML/CSS, (Vanilla) JavaScript, WordPress, Amazon Web Services
\linebreak
Project link: \href{https://giveblood.sg/iron-rich-food/}{https://giveblood.sg/iron-rich-food/}
}

%------------------------------------------------

\cventry
{Front-End Web Developer for \href{https://helloakin.com/}{Techlyon Pte Ltd}} % Job title
{} % Organization
{} % Location
{Feb. 2022 -- Mar. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibility: Build a mini web-based game, i.e. \href{https://giveblood.sg/blood-bag-rush/}{Blood Bag Rush}.
\linebreak
% Most challenging task: to ensure the game can run flawlessly at any screen frame rate.
% \linebreak
Technology stack: HTML/CSS, (Vanilla) JavaScript, WordPress, Amazon Web Services
\linebreak
Project link: \href{https://giveblood.sg/blood-bag-rush/}{https://giveblood.sg/blood-bag-rush/}
}

%------------------------------------------------

\cventry
{Front-End Web Developer for \href{https://helloakin.com/}{Techlyon Pte Ltd}} % Job title
{} % Organization
{} % Location
{June 2021 -- July 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibility: Build an interactive and responsive web page, i.e. \href{https://giveblood.sg/discover/}{The Journey of Blood}.
\linebreak
% Most challenging task: to ensure the web page can run responsively both on desktop and mobile devices, both on non-touch and touch devices, both on potrait and landscape devices.
% \linebreak
Technology stack: HTML/CSS, JavaScript/GSAP, WordPress, Amazon Web Services
\linebreak
Project link: \href{https://giveblood.sg/discover/}{https://giveblood.sg/discover/}
}

%------------------------------------------------

\cventry
{Full-stack Software Engineer for PT Nestlé Indonesia} % Job title
{Freelance} % Organization
{Remote} % Location
{January 2023 -- February 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibility: Build a new page module to the existing website.
\linebreak
Technology stack: PHP/Drupal, JavaScript, MySQL
}

%------------------------------------------------

% \cventry
% {Artificial Intelligence Researcher for Robotics and Artificial Intelligence Laboratory} % Job title
% {} % Organization
% {} % Location
% {June 2019 -- November 2020} % Date(s)
% { % Description(s) of tasks/responsibilities
% Responsibilities:
% \vspace{5mm}
% \begin{cvitems}
% \item {Developing an approach to modelling automatic human emotion recognition on the classroom environments.}
% \item {Writing a scientific article about the research.}
% \end{cvitems}
% \vspace{4mm}
% Technology stack: Python/PyTorch, LaTeX
% }

%------------------------------------------------

\cventry
{Full-Stack Software Engineer for Indonesia University of Education (IUE)} % Job title
{} % Organization
{} % Location
{Feb. 2019 -- Sept. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibilities:
\vspace{5mm}
\begin{cvitems}
\item {Build a mobile-based online tutoring platform, Rumah Cerdas, for internal use only.}
% \item {Build APIs to access the educational content.}
\item {Designing, migrating, and maintaining the database of educational content.}
\end{cvitems}
\vspace{4mm}
Technology stack: Android/Java, Python/Flask, JavaScript, PostgreSQL, Apache, DigitalOcean
}

%------------------------------------------------

\cventry
{Full-Stack Software Engineer for Department of Sociology Education, IUE} % Job title
{} % Organization
{} % Location
{July 2018 -- Feb. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibilities:
\vspace{5mm}
\begin{cvitems}
\item {Build a mobile-based social media platform, Sociology Education Research Application (SERA), for sharing information about local wisdom and local knowledge, for internal use only.}
% \item {Build APIs to access the social content.}
\item {Build content management system for moderating the social content.}
\end{cvitems}
\vspace{4mm}
Technology stack: Android/Java, PHP/CodeIgniter, MySQL, Apache, Google Cloud Platform
}

%------------------------------------------------

% \cventry
% {Software Engineer Volunteer for <Effective Reading Ability>} % Job title
% {Freelancer} % Organization
% {Remote} % Location
% {July 2018} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Programmed a mobile application to practice the effective reading skills of elementary school students.}
% \item {Designed and programmed APIs to process statistical information about the students' reading exercises.}
% \end{cvitems}
% }

%------------------------------------------------

\cventry
{Software Engineer Internship} % Job title
{\href{https://www.indonesian-aerospace.com/}{PT Dirgantara Indonesia}} % Organization
{Bandung, West Java} % Location
{Sept. 2019 -- Nov. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsibility: Research and re-engineering a desktop application for creating aircraft performance graph analysis report documents.
\linebreak
Technology stack: Python/PyQt5
% \linebreak
% Most challenging task: to replicate the document rendering functionality of an existing application and to optimise the font rendering of the current application.
}

%------------------------------------------------

\cventry
{Graphic Designer | Copywriting Editor | Teaching Assistant | Researcher | Public Relations | Organizer} % Job title
{Non-Profit Organizations} % Organization
{Bandung, West Java (Remote)} % Location
{Oct. 2017 -- Present} % Date(s)
{ % Description(s) of tasks/responsibilities
Let's have a conversation to find out more about what benefits I can bring to your company.
}

%------------------------------------------------

% \cventry
% {Volunteer Interface and User Experience Designer} % Job title
% {Tarbiyah Sunnah Foundation} % Organization
% {Remote} % Location
% {December 2020 -- Present} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Researching and designing interfaces and user experiences of an islamic learning application for mobile platforms.}
% \end{cvitems}
% }

%------------------------------------------------

% \cventry
% {Graphic Designer Volunteer} % Job title
% {Halaqah Silsilah Ilmiyyah AbdullahRoy Foundation} % Organization
% {Remote} % Location
% {Oct. 2017 -- July 2018} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Designed da'wah posters.}
% \item {Researching and designing da'wah websites.}
% \item {Edited copywriting for da'wah posters.}
% \end{cvitems}
% }

%------------------------------------------------

\end{cventries}
